Automatic Matching of Bullet Land Impressions

### 2017-06-29 arxiv-submission/imaging-paper.tex
submission final

The smooth curve on the plot represents a segment of a perfect circle with the same radius as the bullet. While the circle is an obvious first choice for fitting the structure, it does not completely capture the bullet surface after it was fired. A discussion of a circular fit and the remaining residual structure can be found in Supplement Section~\ref{supp:cylindrical}.
%It is clear that our next approach must be to model the overall structure in order to focus on the deviations, given that the deviations should correspond to bullet markings.

@@

% AOS,AOAS: If there are supplements please fill:
%\begin{supplement}[id=suppA]
%  \sname{Supplement A}
%  \stitle{Title}
%  \slink[doi]{10.1214/00-AOASXXXXSUPP}
%  \sdatatype{.pdf}"
%  \sdescription{Some text}
%\end{supplement}

>>>>

The smooth curve on the plot represents a segment of a perfect circle with the same radius as the bullet. While the circle is an obvious first choice for fitting the structure, it does not completely capture the bullet surface after it was fired. A discussion of a circular fit and the remaining residual structure can be found in Supplement Section~\ref{supp:cylindrical} \citep{supplement}.
%It is clear that our next approach must be to model the overall structure in order to focus on the deviations, given that the deviations should correspond to bullet markings.

@@

% AOS,AOAS: If there are supplements please fill:
\begin{supplement}[id=suppA]
  \sname{Supplement A}
  \stitle{Supplement to Automatic Matching of Bullet Land Impressions}
  \slink[doi]{COMPLETED BY THE TYPESETTER}
  \sdatatype{.pdf}" 
  \sdescription{Supplementary derivations for Automatic matching of bullet land impressions}
\end{supplement}
